Brain Tumor Detection using Machine Learning Models

### 2021-08-04 slides.tex
added project guide

\author[Rajarshi, Bhargav, Soptorshi, Brahmajit] {
	Bhargav Basu (183313-21-0045) \texorpdfstring{\\} \and
	Soptorshi Bhattacharjee (183313-21-0050) \texorpdfstring{\\} \and
	Brahmajit Das (183313-21-0044) \texorpdfstring{\\} \and
	Rajarshi Sardar (183313-21-0055)
}

>>>>

\author[Rajarshi, Bhargav, Soptorshi, Brahmajit] {
	Bhargav Basu (183313-21-0045) \texorpdfstring{\\} \and
	Soptorshi Bhattacharjee (183313-21-0050) \texorpdfstring{\\} \and
	Brahmajit Das (183313-21-0044) \texorpdfstring{\\} \and
	Rajarshi Sardar (183313-21-0055 \texorpdfstring{\\ \vspace{1cm}}) \and
	Project Guide: Prof. \textbf{Kajari Bhattacharjee}
}
